A fast and memory-efficient transition state search method for complex energy landscapes \\ Supplementary Information

### 2022-05-12 si/supplementary_information.tex
Put distance and pair energy in results. Made Jack's changes.
Added highest TS test to SI

\documentclass[aps,physrev,10pt]{revtex4-2}

@@

\begin{document}
\title{Binary Image Transition State Search \\ Supplementary Information}
\author{Samuel J. Avis}
\author{Jack R. Panter}
\email[]{j.r.panter@durham.ac.uk}
\author{Halim Kusumaatmaja}
\email[]{halim.kusumaatmaja@durham.ac.uk}
\affiliation{Department of Physics, Durham University, South Road, Durham DH1 3LE, UK}
\maketitle

@@

>>>>

\documentclass[10pt]{revtex4}

% Text
% \usepackage{amssymb}

@@

\begin{document}
\title{A fast and memory-efficient transition state search method for complex energy landscapes \\ Supplementary Information}
\author{Samuel J. Avis}
\author{Jack R. Panter}
\email[]{j.r.panter@durham.ac.uk}
\author{Halim Kusumaatmaja}
\email[]{halim.kusumaatmaja@durham.ac.uk}
\affiliation{Department of Physics, Durham University, South Road, Durham DH1 3LE, UK}
\maketitle

@@

\section{Multiple transition states}
Here we test how the BITSS method performs when there are multiple transition states in the pathway between the two starting minima.
For this we use a 2D potential, shown in \cref{fig:multits}a, with a pathway that follows a chicane of two $135^\circ$ circular arcs.
The energy is given by the squared distance from this path, plus two barriers resulting in transition states A and B, with energies $E_A$ and $E_B$.
We then vary $E_B$ between 0 and $E_A$, and the size of the distance reduction factor, $f$, to see if BITSS successfully converges to the higher transition state A.
For each pair of parameters we perform 5 runs with slight variations in the starting positions, with the results in \cref{fig:multits}b showing the points at which all 5 converge to A.

We see that if the difference between the two barriers is sufficiently large ($\gtrsim 10\%$) then BITSS always converges to the higher transition state.
However, as the difference decreases it starts to sometimes converge to the lower transition state if the separation is decreased quickly.
Therefore, to ensure that BITSS always converges to the higher energy transition state it may be necessary to restrict the separation step size.

Although the equal-energy constraint should cause the states to converge to A, this is not always the case because the discrete steps in the minimisation can cause the left image to jump over A before the other image passes B.
If the minisation is fast and takes large steps then the chance for this to occur is increased.
Therefore, systems with complex, high-dimensional landscapes can probably successfully locate the highest transition state for larger values of $f$ and smaller height differences than simpler systems such as this 2D example.

\begin{figure}[htb]
  \includegraphics{fig/multits.pdf}
  \caption{\label{fig:multits}
    (a) The potential used in the test.
    M1 and M2 denote the two starting minima, and A and B are the two transition states.
    The energy of the barrier to B, $E_B$, is varied between 0 and $E_A$.
    (b) The results for the parameters under which BITSS reliably converges to A, and the points at which it sometimes converges to B.
    The x-axis is the BITSS distance reduction factor, $f$, and the y-axis is the relative difference between the two barrier heights.
  }
\end{figure}
